```{r}
library(brms)
library(magrittr)
library(ggplot2)
library(tidyr)
library(faux)
library(tidybayes)
library(dplyr)
library(mediation)
```

## Generate the design

```{r}

gen_data <- function(seed,n){
  set.seed(seed)
 between <- list(P = c("negative","neutral","positive"))
 
 df <- sim_design(list(), between, n = n,plot=FALSE)
 df$PF  = runif(nrow(df))
 df$dPO = runif(nrow(df))#rep(1:5,nrow(df)/5)
 df$J1  = runif(nrow(df))#rep(1:5,nrow(df)/5)
 df$J2  = runif(nrow(df))#rep(1:5,nrow(df)/5)
 df$J3  = runif(nrow(df))#rep(1:5,nrow(df)/5)
 df$J4  = runif(nrow(df))#rep(1:5,nrow(df)/5)
 df
}
df = gen_data(1,100) # 100 subjects per group
head(df)
```

## Define the model

```{r}
 
 library(brms)
 model_mediator1 <- bf(PF ~ 0+P)
 #model_mediator2 <- bf(J1 ~ 1+P + PF, family = cumulative("logit"))
 model_mediator2 <- bf(J1 ~ 0+P + PF)
 model_mediator3 <- bf(J2 ~ 0+P + PF)
 model_mediator4 <- bf(J3 ~ 0+P + PF)
 model_mediator5 <- bf(J4 ~ 0+P + PF)
 model_outcome  <- bf(dPO ~ 0+P + PF + J1+J2+J3+J4)#, family = cumulative("logit"))
```

## Define the priors

```{r}
priors = c(
     prior(normal( 0.2,0.01), coef = "Pnegative",resp="PF"),
     prior(normal( 0.0,0.01), coef = "Pneutral",resp="PF"), 
     prior(normal(-0.2,0.01), coef = "Ppositive",resp="PF"),
     
     prior(normal(-0.5,0.01), coef = "Pnegative",resp="J1"),
     prior(normal( 0.0,0.01), coef = "Pneutral",resp="J1"),
     prior(normal( 0.5,0.01), coef = "Ppositive",resp="J1"),
     prior(normal(-1.0,0.01), coef = "PF",resp="J1"),
     
          
     prior(normal(-0.5,0.01), coef = "Pnegative",resp="J2"),
     prior(normal( 0.0,0.01), coef = "Pneutral",resp="J2"),
     prior(normal( 0.5,0.01), coef = "Ppositive",resp="J2"),
     prior(normal(-1.0,0.01), coef = "PF",resp="J2"),
     
     
          
     prior(normal(-0.5,0.01), coef = "Pnegative",resp="J3"),
     prior(normal( 0.0,0.01), coef = "Pneutral",resp="J3"),
     prior(normal( 0.5,0.01), coef = "Ppositive",resp="J3"),
     prior(normal(-1.0,0.01), coef = "PF",resp="J3"),
     
     
          
     prior(normal(-0.5,0.01), coef = "Pnegative",resp="J4"),
     prior(normal( 0.0,0.01), coef = "Pneutral",resp="J4"),
     prior(normal( 0.5,0.01), coef = "Ppositive",resp="J4"),
     prior(normal(-1.0,0.01), coef = "PF",resp="J4"),
     
     
     prior(normal(-0.25,0.01), coef = "Pnegative",resp="dPO"),
     prior(normal( 0.0 ,0.01), coef = "Pneutral",resp="dPO"),
     prior(normal( 0.25,0.01), coef = "Ppositive",resp="dPO"),
     
     prior(normal( 1.,0.01), coef = "J1",resp="dPO"), #
     prior(normal( 1.,0.01), coef = "J2",resp="dPO"), #
     prior(normal( 1.,0.01), coef = "J3",resp="dPO"), #
     prior(normal( 1.,0.01), coef = "J4",resp="dPO"), #

     prior(normal( 0 ,0.01), coef = "PF",resp="dPO"),
   
     prior(normal(0,1), class = "sigma",resp="dPO"),
     prior(normal(0,1), class = "sigma",resp="J1"),
     prior(normal(0,1), class = "sigma",resp="J2"),
     prior(normal(0,1), class = "sigma",resp="J3"),
     prior(normal(0,1), class = "sigma",resp="J4"),
     prior(normal(0,1), class = "sigma",resp="PF")
   )
```

## Sample parameters from the prior

We once need to sample the model to get the actual parameters. We can reuse the model later to fit those parameters and check how often we can come to the correct conclusions

```{r}
#| output: false
 # J1 => Truth
 # J2 => Trust
 # J3 => Familiarity
 # J4 => Likeability
 med_prior = brm(
   model_mediator1 + model_mediator2  + model_mediator3 + model_mediator4 +  model_mediator5+ model_outcome + set_rescor(FALSE), 
   prior = priors,
   data = df, sample_prior="only",cores=4,chains=4,refresh=0)

med_model = brm(
   model_mediator1 + model_mediator2 + model_mediator3 + model_mediator4 +  model_mediator5 + model_outcome + set_rescor(FALSE), 
   data = df,cores=4,chains=4,refresh=0)
```

## Generate a single prediction

::: {callout-note}
We are using the mean prior value here (`summary=TRUE`) - later we will use single draws from the posterior.
:::

```{r}


#sim_y2 = predict(med_prior,summary=TRUE)

f_pf = fitted(med_prior,newdata=data.frame(P=df$P),resp="PF")
f_j1 = fitted(med_prior,newdata=data.frame(P=df$P,PF=f_pf[,1]),resp="J1")
f_j2 = fitted(med_prior,newdata=data.frame(P=df$P,PF=f_pf[,1]),resp="J2")
f_j3 = fitted(med_prior,newdata=data.frame(P=df$P,PF=f_pf[,1]),resp="J3")
f_j4 = fitted(med_prior,newdata=data.frame(P=df$P,PF=f_pf[,1]),resp="J4")


f_dpo = fitted(med_prior,newdata=data.frame(P=df$P,PF=f_pf[,1],J1=f_j1[,1],J2=f_j2[,1],J3=f_j3[,1],J4=f_j4[,1]),resp="dPO")


#sim_y = predict(med_prior,newdata=data.frame(P=df$P))


df_prior = data.frame(P=df$P,PF=f_pf[,1],J1=f_j1[,1],J2=f_j2[,1],J3=f_j3[,1],J4=f_j4[,1],dPO=f_dpo[,1])
head(df_prior)
```
```{r}
o = df_prior %>% group_by(P) %>% summarise(avg=mean(dPO))
diff(o$avg)
```
```{r}
med_prior
```

## Initial Plotting

```{r}
ggplot(df_prior,aes(x=P,y=dPO))+geom_point(alpha=0.2) + stat_summary(color="red")

ggplot(df_prior,aes(x=P,y=dPO))+stat_summary(position=position_nudge(x=0.1))+geom_point(alpha=0.2)

ggplot(df_prior,aes(x=PF,color=P))+geom_density()

ggplot(df_prior,aes(x=PF))+geom_histogram()

ggplot(df_prior,aes(x=J1,color=P))+geom_density()

ggplot(df_prior,aes(y=J1,x=PF,color=PF))+geom_point()

ggplot(df_prior,aes(y=dPO,x=J1,color=PF))+geom_point()+facet_grid(0~P)

```
## Power analysis

```{R}
#| output: false

n_sim <- 10
n <- 200


pred_data = function(seed,d_new,sim_y){
  message(seed)
  df_prior = d_new
  
  df_prior$PF= sim_y[seed,,"PF"]
  df_prior$J1= sim_y[seed,,"J1"]
  df_prior$J2= sim_y[seed,,"J2"]
  df_prior$J3= sim_y[seed,,"J3"]
  df_prior$J4= sim_y[seed,,"J4"]
  df_prior$dPO= sim_y[seed,,"dPO"]
  df_prior
}

sims <- tibble(seed = 1:n_sim)

d_new = gen_data(1,n=n)
sim_y = posterior_predict(med_prior,newdata = d_new)
sims = sims %>% rowwise() %>% mutate(d=list(pred_data(seed,d_new,sim_y)))

sims = sims%>% rowwise()%>%mutate(brms = list(update(med_model,newdata = d,seed=seed)))
  
```

```{r}
#library(tidybayes)
#med_prior %>%
#  spread_draws() %>%
#  ggplot(aes(y = condition, x = condition_mean)) +
#  stat_halfeye()
```